Comparison of canopy height measurement between TLS and Sentinel2 data

### 2023-07-20 submission_3/UAV+S2.qmd
Adds links to src code

---
title: "UAV vs Sentinel-2 height comparisons"
subtitle: "Documentation"
author: "Fabian Götz"
date: 6/24/23
format:
    pdf:
        documentclass: scrreport
        theme: united
        toc: true
        toc-depth: 2
        number-sections: true
        number-depth: 1
        toc-title: Table of Contents
        toc-location: body
        colorlinks: true
header-includes:  
- \usepackage{graphicx}
- \usepackage{lscape}
- \usepackage{array}
---

@@

As the figures in Figure 1.1 - 1.3 show, the UAV estimates differ significantly from those of the S2 data. UAV peak height per pixel shows a scale with a maximum of 35 and a minimum of 0. In comparison, S2 peak height per pixel shows only a maximum of 33 and a minimum of 26. Thus, the range of UAV values is much larger. This suggests a much finer spatial resolution leading to the differences. This confirms what we have already learned, that UAV is able to record at a finer spatial resolution than satellites are able to, due to their distance. Thus, we assume that UAV are closer to ground truth than Sentinel-2. While the histograms show the general distribution of the data, the maps allow us to see the distributions based on the coordinates. In the map of the residuals it can be seen in another way that the measured values of the two measurement methods are different. Specifically, one can see that Sentinel-2 does not resolve accurately enough to detect locations with low tree heights. Thus, the values of Sentinel-2 are too high on average.

>>>>

---
title: "UAV vs Sentinel-2 height comparisons"
subtitle: "Documentation"
author:  
    # - **Group 4** 
    - Denis Streitmatter 
    - Marie-Louise Korte 
    - Louis Trinkle 
    - Maxwell Sivertsen 
    - Fabian Götz 
    - Lukas Erzfeld
date: 6/24/23
format:
    pdf:
        documentclass: scrreport
        theme: united
        toc: false
        toc-depth: 2
        number-sections: true
        number-depth: 1
        toc-title: Table of Contents
        toc-location: body
        colorlinks: true
header-includes:  
- \usepackage{graphicx}
- \usepackage{lscape}
- \usepackage{array}
---

@@

As the figures in Figure 1.1 - 1.3 show, the UAV estimates differ significantly from those of the S2 data. UAV peak height per pixel shows a scale with a maximum of 35 and a minimum of 0. In comparison, S2 peak height per pixel shows only a maximum of 33 and a minimum of 26. Thus, the range of UAV values is much larger. This suggests a much finer spatial resolution leading to the differences. This confirms what we have already learned, that UAV is able to record at a finer spatial resolution than satellites are able to, due to their distance. Thus, we assume that UAV are closer to ground truth than Sentinel-2. While the histograms show the general distribution of the data, the maps allow us to see the distributions based on the coordinates. In the map of the residuals it can be seen in another way that the measured values of the two measurement methods are different. Specifically, one can see that Sentinel-2 does not resolve accurately enough to detect locations with low tree heights. Thus, the values of Sentinel-2 are too high on average.^[The source code for all plots can be found at [https://github.com/yum-yab/ground_truthing_module/blob/main/submission_3/uav_s2_height_comparison.r](https://github.com/yum-yab/ground_truthing_module/blob/main/submission_3/uav_s2_height_comparison.r)]

### 2023-07-20 submission_4/submission_4.qmd
Adds links to src code

---
title: "Comparison of canopy height mesurment between TLS and Sentinel2 data"
subtitle: "Documentation"
subsubtitle: "Leaf traits measurements"
# Ok I reallly dont know why this does not work, 
# author: | 
#     | **Group 4** 
#     | Denis Streitmatter 
#     | Marie-Louise Korte 
#     | Louis Trinkle 
#     | Maxwell Sivertsen 
#     | Fabian Götz 
#     | Lukas Erzfeld
author:  
    # - **Group 4** 
    - Denis Streitmatter 
    - Marie-Louise Korte 
    - Louis Trinkle 
    - Maxwell Sivertsen 
    - Fabian Götz 
    - Lukas Erzfeld
date: last-modified
format:
    pdf:
        documentclass: scrreport
        theme: united
        toc: false
        toc-depth: 2
        number-sections: false 
        number-depth: 1
        toc-title: Table of Contents
        toc-location: body
        colorlinks: true
header-includes:  
- \usepackage{graphicx}
- \usepackage{lscape}
- \usepackage{array} 
---

@@

1. TLS measurement was carried out at breast height
2. Preprocessing of the TLS data via CloudCompare^[See [https://www.cloudcompare.org/](https://www.cloudcompare.org/)]
3. QGIS was used for visualizing the sentinel data and creating the area of interest
4. `R` was used to resample the TLS data to match the resolution of the Sentinel data
5. `R` was also used to calculate the residuals and generally producing all figures in this document (importing the results of step 2, 3 and 4)

>>>>

---
title: "Comparison of canopy height measurement between TLS and Sentinel2 data"
subtitle: "Documentation"
subsubtitle: "Leaf traits measurements"
# Ok I reallly dont know why this does not work, 
# author: | 
#     | **Group 4** 
#     | Denis Streitmatter 
#     | Marie-Louise Korte 
#     | Louis Trinkle 
#     | Maxwell Sivertsen 
#     | Fabian Götz 
#     | Lukas Erzfeld
author:  
    # - **Group 4** 
    - Denis Streitmatter 
    - Marie-Louise Korte 
    - Louis Trinkle 
    - Maxwell Sivertsen 
    - Fabian Götz 
    - Lukas Erzfeld
date: last-modified
format:
    pdf:
        documentclass: scrreport
        theme: united
        toc: false
        toc-depth: 2
        number-sections: false 
        number-depth: 1
        toc-title: Table of Contents
        toc-location: body
        colorlinks: true
header-includes:  
- \usepackage{graphicx}
- \usepackage{lscape}
- \usepackage{array} 
---

@@

1. TLS measurement was carried out at breast height
2. Preprocessing of the TLS data via CloudCompare^[See [https://www.cloudcompare.org/](https://www.cloudcompare.org/)]
3. QGIS was used for visualizing the sentinel data and creating the area of interest
4. `R` was used to resample the TLS data to match the resolution of the Sentinel data
5. `R` was also used to calculate the residuals and generally producing all figures in this document (importing the results of step 2, 3 and 4)^[The code for everything can be found here [https://github.com/yum-yab/ground_truthing_module/blob/main/submission_4/TLS_plots/TLS_plots.R](https://github.com/yum-yab/ground_truthing_module/blob/main/submission_4/TLS_plots/TLS_plots.R)]
